### 2014-02-24 paper/retrofit.tex
Fix tau.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
tt   ::= bool | tt -> tt | ref tt
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

>>>>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
tty   ::= bool | tty -> tty | ref tty
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE
